### 2023-02-10 doc/manuscript/translocation.qmd
Fix author affiliation superscript
Edits to outline of introduction

Roland A. Knapp^1,2^\*, Mark Q. Wilber^3^, Allison Q. Byrne^4,5^, Maxwell B. Joseph^6,7^, Thomas C. Smith^1,2^, Andrew P. Rothstein^3,4^, Rob L. Grasso^8^, Erica Bree Rosenblum^4,5^

@@

-   Important for conservation action, evolutionary rescue not only promotes recoveries of focal populations, but can also provide sources of resistant individuals to reestablish populations extirpated following disease emergence (Mendelson et al. 2019, Joseph and Knapp 2018).

@@

-   Translocation of individuals from putatively resistant populations to sites that were formerly occupied but from which populations were extirpated by disease provides a way to disentangle the contributions of natal environment and host genetics on host persistence and recovery.

@@

@@

We then use genetic evidence to demonstrate that observed disease resistance is likely a result of selection and provide five lines of evidence that evolutionary rescue is a strong candidate mechanism for emergence of this resistance.

<!--# These bullet points might be better addressed in the Discussion than in the Introduction. -->

@@

>>>>

Roland A. Knapp^1,2^\*, Mark Q. Wilber^3^, Allison Q. Byrne^4,5^, Maxwell B. Joseph^6,7^, Thomas C. Smith^1,2^, Andrew P. Rothstein^4,5^, Rob L. Grasso^8^, Erica Bree Rosenblum^4,5^

@@

-   Evolutionary rescue be difficult to detect, and this complicates our understanding of the potential importance of evolutionary rescue in allowing the persistence and recovery of host populations following disease emergence (Eskew et al. 2021, Lilley et al. 2020). <!--# Maybe move this to the Discussion? -->

-   Important for conservation action, evolutionary rescue not only promotes recoveries of focal populations (Gignous-Wolfsohn et al. 2021), but can also provide sources of resistant individuals to reestablish populations extirpated following disease emergence (Mendelson et al. 2019, Joseph and Knapp 2018).

@@

-   Translocation of individuals from putatively resistant <!--# Can we use "reduced susceptibilty" strategically to avoid potential pitfalls associated with resistance, tolerance, and our lack of understanding of what actual mechanism underlyies lower Bd loads and higher frog survival?  --> populations to sites that were formerly occupied but from which populations were extirpated by disease provides a way to disentangle the contributions of natal environment and host genetics on host persistence and recovery.

@@

-   <!--# Zooming out here to make a broader point --> Few, if any, studies of disease-impacted species have provided comprehensive evidence that (1) evolutionary rescue can increase host resistance, (2) increased host resistance contributes to higher individual fitness (e.g., survival) in the presence of disease and allows population growth, (3) higher individual fitness and positive population growth applies beyond the natal environment, (4) individuals from higher-fitness populations can be used in translocations to reestablish extirpated populations, and (5) many reestablished populations have a high probability of persisting over the long term in a landscape of disease. <!--# I don't know how many of these boxes we can check, but they seem like important points to help us lay the foundation for our study (which checks more of these boxes than do most studies). I actually wonder if taking the broader approach outlined in this bullet would make for a more compelling argument than one focused more narrowly on issue #3, as most of the bullets in this paragraph currently do. That issue, although important, may distract from the broader perspective that I tried to highlight. -->

@@

We then use genetic evidence to demonstrate that observed disease resistance is likely a result of selection.

@@

We provide five lines of evidence that evolutionary rescue is a strong candidate mechanism for emergence of this resistance. <!--# Consider broadening the scope of this sentence and the paragraph to be developed from it to encompass all of our findings -->
